\thesistitle

### 2019-06-11 sections/research.tex
Added called methods example

>>>>

Because of this, for type 1R clones, we compare the fully qualified method signature for all method references. A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments. For instance, an \texttt{eat} method could become \texttt{java.lang.Boolean com.simonbaars.fruitgame.Apple.eat(java.util.List<com.simonbaars.fruitgame.tools.Tool>)}.
